Bayesian multivariate skew-normal finite mixture model for analysis of infant development trajectories

### 2019-06-24 manuscript/manuscript.tex
section 3

\subsection{Conditional MSN Imputation}
To accommodate missing at random (MAR) responses, we propose a convenient imputation algorithm that can be implemented ``online'' as part of the Gibbs sampler. In Section 6, we discuss extension to allow for non-ignorable missingness. Suppose $\mathbf{y}_i$ has $q_i\in (1,\ldots,J)$ observed values, denoted $\mathbf{y}^{obs}_i$, and $J-q_i$ intermittent missing values, denoted $\mathbf{y}^{miss}_i$. We can use of the stochastic representation given in equation (\ref{eq:msnreg}) to impute $\mathbf{y}^{miss}_i$ from its conditional multivariate normal distribution given $(z_i,t_i,Y^{obs}_i)$:
\begin{eqnarray}
\mathbf{y}^{miss}_i|(z_i=k,t_i,\mathbf{y}^{obs}_i)&\sim& N_{J-q}(\boldsymbol\mu^{miss}_{ik},\boldsymbol\Sigma^{miss}_k),~\text{where}\nonumber\\
\boldsymbol\mu^{miss}_{ik}&=&\\
\boldsymbol\Sigma^{miss}_k&=& \nonumber
\end{eqnarray}
\textbf{Carter -- work on the above -- you will need to define notation and refer readers back to equation (3) as needed. We can discuss next week if needed}
These results follow from conventional multivariate normal theory. An attractive feature of this imputation algorithm is that it provides more opportunities to explore the parameter space than multiple imputation \textbf{[based on summary stats right?]} and avoids multiplicative run-time scaling in $m$, the number of imputations \textbf{Give refs}. In Section 4, we conduct simulation studies to demonstrate that imputing the missing MSN responses improves inferences over complete case analysis.

@@

\end{itemize}
\end{document}

>>>>

\subsection{Conditional MSN Imputation}
To accommodate missing at random (MAR) responses, we propose a convenient imputation algorithm that can be implemented ``online'' as part of the Gibbs sampler. In Section 6, we discuss extensions to allow for non-ignorable missingness. Suppose $\mathbf{y}_i$ has $q_i\in (1,\ldots,J)$ observed values, denoted $\mathbf{y}^{obs}_i$, and $J-q_i$ intermittent missing values, denoted $\mathbf{y}^{miss}_i$. We can make use of the stochastic representation given in equation (\ref{eq:msnreg}) to impute $\mathbf{y}^{miss}_i$ from its conditional multivariate normal distribution given $(z_i,t_i,Y^{obs}_i)$:
\begin{eqnarray}
\mathbf{y}^{miss}_i|(z_i=k,t_i,\mathbf{y}^{obs}_i)&\sim& N_{J-q}(\boldsymbol\mu^{miss}_{ki},\boldsymbol\Sigma^{miss}_k),~\text{where}\nonumber\\
\boldsymbol\mu^{miss}_{ki}&=&\\
\boldsymbol\Sigma^{miss}_k&=& \nonumber
\end{eqnarray}
\textbf{Carter -- work on the above -- you will need to define notation and refer readers back to equation (3) as needed. We can discuss next week if needed}
These results follow from conventional multivariate normal theory. An attractive feature of this imputation algorithm is that it provides more opportunities to explore the parameter space than multiple imputation \textbf{[based on summary stats right?]} and avoids multiplicative run-time scaling in $m$, the number of imputations \textbf{Give refs}. In Section 4, we conduct simulation studies to demonstrate that imputing the missing MSN responses improves inferences over complete case analysis.

@@
